An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-17 main.tex
Remove comments about antibacterial resistance.
Also remove %todo about contributions (it's currently in the README of
the repo and will/can be added to the paper depending on the journal?).

Recent work has argued that agent-based
simulations can provide insights in evolutionary game theory not available
via direct mathematical analysis \cite{adami2016evolutionary}. The results
and insighed contained in this paper would be difficult to derive analytically.

@@

These finding have the potential to offer insight in to organisms such as antibacterial
resistant bacteria \cite{Davies2010} and human social behaviors.

@@

% TODO: author contributions

>>>>

Recent work has argued that agent-based
simulations can provide insights in evolutionary game theory not available
via direct mathematical analysis \cite{adami2016evolutionary}. The results
and insights contained in this paper would be difficult to derive analytically.

@@

@@
